\replaced{Towards an open-source landscape for 3D CSEM modelling}{Open-source landscape for 3D CSEM modelling}

### 2021-01-05 manuscript/Manuscript.tex
Start revision seriously

\title[3D CSEM Open-Source Landscape]{Open-source landscape for 3D CSEM modelling}

\author[D. Werthmüller \emph{et al.}]
  {\Large Dieter Werthmüller$^1$,        % orcid: 0000-0002-8575-2484
   Raphael Rochlitz$^2$,          % orcid: 0000-0002-5132-916X
   Octavio Castillo-Reyes$^3$ and % orcid: 0000-0003-4271-5015
   Lindsey Heagy$^4$              % orcid: 0000-0002-1551-5926
   \\
   \footnotesize
  $^1$ TU Delft, Building 23, Stevinweg 1 / PO-box 5048, 2628 CN Delft (NL).
  E-mail: \href{mailto:Dieter@Werthmuller.org}{Dieter@Werthmuller.org}\\[-.3em]
   \footnotesize
  $^2$ Leibniz Institute for Applied Geophysics, Stilleweg 2, 30655 Hannover (DE)\\[-.3em]
   \footnotesize
   $^3$ Barcelona Supercomputing Center (BSC), Nexus II Building c/Jordi Girona, 29, 08034 Barcelona (ES)\\[-.3em]
   \footnotesize
  $^4$ University of California Berkeley, Department of Statistics (USA)
  }

@@

% % == Notes from Wim; to incorporate ==
%
% All implemented
%
% % == Notes form Paulo ==
%
% Very good to know that the Ex responses are well represented. For most of the inversions done in the industry, we use these fields only.
%
% Ez: the mismatch occurs at the longer offsets and below the noise threshold 10-15. EMGS argues now that with the new source, the threshold is pushed to 10-16. But in practice, if the curve follows a smooth decay, we use this data for inversion, and we get meaningful geological results compared to seismic images.
%
% Ey: the broadside component is quite close,  with small differences at long offsets. For the inline component, I've noted that your responses are up to two orders of magnitude higher than MR3D. The four programs you tested give the same amplitudes? It may be a problem with the EMGS software, as EY is always neglected we may have ignored that issue. Simultaneously, it looks that your inline responses are at the same level as the broadside ones.
%
% Bathymetry is also a big issue. It must be well represented to avoid problems.
%
% % == Notes from Evert ==
%
% [T]he fact that the solutions in the four codes are roughly correct with an expected error between 1\% and 10\% makes it totally understandable that the field that is one to two orders of magnitude smaller has no accuracy. You could test this by driving the overall error down by a factor 100. Not sure that is feasible with all codes but if you can do it with one it can be enough when all codes agree sufficiently on the strong field components. Another option can be to increase the cross line component in the error computation.

@@

\begin{itemize}
  \item \deleted{old}: \texttt{\textbackslash deleted\{old\}}
  \item \added{new}: \texttt{\textbackslash added\{new\}}
  \item \replaced{new}{old}: \texttt{\textbackslash replaced\{new\}\{old\}}
\end{itemize}

@@

We briefly present our codes in this section. It is, however, beyond the scope of this article to go into every detail of the different modellers, and we refer to their documentations for more details. An overview comparison of the codes is given in Table~\ref{tbl:codecomparison}. All four have in common that they solve Maxwell's equation in its differential form (DE) under the quasi-static or diffusive approximation, hence neglecting displacement currents, which is a common approximation for the low frequency range usually applied in CSEM. The machines on which the different codes were run are listed in Table~\ref{tbl:machines} together with the responsible operator. A few clarifying words on abbreviations and definitions: For the boundary conditions (BC) in the comparison table we use the abbreviations \emph{PEC} and \emph{PMC}, which stand for perfect electric conductor
% We could add maths here; but we would need to introduce all the symbols. For now, we leave it out.
% ($\vec{n}\times\vec{E} = 0; \vec{n}\cdot\vec{H} = 0$)
and perfect magnetic conductor%
% ($\vec{n}\cdot\vec{E} = 0; \vec{n}\times\vec{H} = 0$)
, respectively. Another abbreviation used in the tables is \emph{dof} for degree of freedom, which is equivalent to the size of the SLE we are solving. Finally, we use \emph{runtime} as the wall time or elapsed real-world time from start to end of solving the SLE; pre- and post-processing (e.g., mesh generation) is not measured. Note that the actual computation time or CPU time is therefore much higher than the reported runtime for the codes that run in parallel, with an upper limit of \#Procs$\times$Runtime. Memory refers to the maximum memory increase at any point of solving the SLE.

>>>>

\title[3D CSEM Open-Source Landscape]{\replaced{Towards an open-source landscape for 3D CSEM modelling}{Open-source landscape for 3D CSEM modelling}}

\author[D. Werthmüller \emph{et al.}]
  {\Large Dieter Werthmüller$^1$, % orcid: 0000-0002-8575-2484
   Raphael Rochlitz$^2$,          % orcid: 0000-0002-5132-916X
   Octavio Castillo-Reyes$^3$ and % orcid: 0000-0003-4271-5015
   Lindsey Heagy$^4$\\            % orcid: 0000-0002-1551-5926
   \footnotesize
  $^1$ TU Delft, Building 23, Stevinweg 1 / PO-box 5048, 2628 CN Delft (NL).
  E-mail: \href{mailto:Dieter@Werthmuller.org}{Dieter@Werthmuller.org}\\[-.3em]
   \footnotesize
  $^2$ Leibniz Institute for Applied Geophysics, Stilleweg 2, 30655 Hannover (DE)\\[-.3em]
   \footnotesize
   $^3$ Barcelona Supercomputing Center (BSC), Nexus II Building c/Jordi Girona, 29, 08034 Barcelona (ES)\\[-.3em]
   \footnotesize
  $^4$ University of California Berkeley, Department of Statistics (USA)
  }

@@

@@

% TODO delete before re-submission
\begin{itemize}
  \item \deleted{old}: \texttt{\textbackslash deleted\{old\}}
  \item \added{new}: \texttt{\textbackslash added\{new\}}
  \item \replaced{new}{old}: \texttt{\textbackslash replaced\{new\}\{old\}}
\end{itemize}

@@

We briefly present our codes in this section. It is, however, beyond the scope of this article to go into every detail of the different modellers, and we refer to their documentations for more details. An overview comparison of the codes is given in Table~\ref{tbl:codecomparison}. All four have in common that they solve Maxwell's equation in its differential form (DE) under the quasi-static or diffusive approximation, hence neglecting displacement currents, which is a common approximation for the low frequency range usually applied in CSEM. \added{For the shown numerical examples all codes use the total-field formulation for the electric field.} The machines on which the different codes were run are listed in Table~\ref{tbl:machines} together with the responsible operator. A few clarifying words on abbreviations and definitions: For the boundary conditions (BC) in the comparison table we use the abbreviations \emph{PEC} and \emph{PMC}, which stand for perfect electric conductor
% We could add maths here; but we would need to introduce all the symbols. For now, we leave it out.
% ($\vec{n}\times\vec{E} = 0; \vec{n}\cdot\vec{H} = 0$)
and perfect magnetic conductor%
% ($\vec{n}\cdot\vec{E} = 0; \vec{n}\times\vec{H} = 0$)
, respectively. Another abbreviation used in the tables is \emph{dof} for degree of freedom, which is equivalent to the size of the SLE we are solving. Finally, we use \emph{runtime} as the wall time or elapsed real-world time from start to end of solving the SLE; pre- and post-processing (e.g., mesh generation) is not measured. Note that the actual computation time or CPU time is therefore much higher than the reported runtime for the codes that run in parallel, with an upper limit of \#Procs$\times$Runtime. Memory refers to the maximum memory increase at any point of solving the SLE.
